A perfect storm and the natural endowments of trade-enabling infrastructure

### 2024-04-18 Slides/20min/20min.Rmd
Rewriting mechanism section
Update slides

@@

---
### But can this explain the population growth?

**Labor force as share of total pop:**
```{r echo=FALSE, out.width="70%", fig.align='center'}
knitr::include_graphics("Figures/all_occupations_share.png")
```

@@

---
### Safer, more convenient harbours
![Skudehandel](Figures/Wikimedia_skudehandel.jpg)
*Dangerous loading on the west coast*

@@

.pull-left[
- Data censuses 1787-1901 contain occupational for some years (3.7 mio. observations) 
- Training data to train an automatic HISCO-label AI for all 12.4 mio. records. 
- Precision: 97.21%; Recall: 97.07% 
- Separate paper - please let me know if you have data
]

.pull-right[
#### How it is applied here
- Top 100 occupations are manually labelled as 'Fishing' or 'Manufacturing'
- Used in a mediation analysis: Can either explain away the effect of the channel?  
- Manufacturing can! 
]

>>>>

---
### From the exhibition at the London Canal Museum
![CanalMuseum](Figures/CanalMuserumLondon.jpg)

@@

@@

@@

.pull-left[
- Censuses 1787-1901 contain HISCO for some years (3.7 mio. observations) 
- Training data $\rightarrow$ 13.5 mio. records. 
- Accuracy: 94 pct + Multlingual
]

.pull-right[
- Check out [OccCANINE](https://github.com/christianvedels/OccCANINE)
- [arXiv: Breaking the HISCO Barrier: Automatic Occupational Standardization with OccCANINE](https://arxiv.org/abs/2402.13604)
w. Christian M. Dahl and Torben Johansen
]
